Growing libraries of concepts with wake-sleep program induction

### 2018-07-23 talk.tex
Sequences unfolding and XKCD (?)

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\begin{frame}{Turtle graphics --- Some results}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalk.eps}
\end{frame}

@@

>>>>

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\begin{frame}{Turtle graphics --- Learning curves and dreams}
  \centering
  \includegraphics[width=9cm]{figures/dreams/montageTalk.eps}
\end{frame}

\begin{frame}{Turtle graphics --- Improved DSL}
  \begin{itemize}
    \item $\frac\pi2$ and $\frac\pi4$ from $\pi$, $2$, $+$ and $/$
    \item A line of length \texttt{n} followed with a right angle
    \item Loops of length \texttt{n} that uses the number \texttt{n} inside.
    \item Unit line then teleport back to origin
    \item ...
  \end{itemize}
\end{frame}

\begin{frame}{Turtle graphics --- All the way down}
  \centering
  \begin{center}
  \only<1>{
    \begin{figure}
      \includegraphics[width=5cm]{figures/teachLogo/star5_black.eps}
    \end{figure}
  }
  \only<2>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_colour.eps}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq2.eps}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq3.eps}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq4.eps}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq5.eps}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<9>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq2.eps}
    \end{figure}
  }
  \only<10>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq3.eps}
    \end{figure}
  }
  \only<11>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq4.eps}
    \end{figure}
  }
  \only<12>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq5.eps}
    \end{figure}
  }
  \only<13>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<14>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp000.png}
    \end{figure}
  }
  \only<15>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp002.png}
    \end{figure}
  }
  \only<16>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp004.png}
    \end{figure}
  }
  \only<17>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp006.png}
    \end{figure}
  }
  \only<18>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp008.png}
    \end{figure}
  }
  \only<19>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp010.png}
    \end{figure}
  }
  \only<20>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp012.png}
    \end{figure}
  }
  \only<21>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp014.png}
    \end{figure}
  }
  \only<22>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp016.png}
    \end{figure}
  }
  \only<23>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp018.png}
    \end{figure}
  }
  \only<24>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp020.png}
    \end{figure}
  }
  \only<25>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp022.png}
    \end{figure}
  }
  \only<26>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp024.png}
    \end{figure}
  }
  \only<27>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp026.png}
    \end{figure}
  }
  \only<28>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp028.png}
    \end{figure}
  }
  \only<29>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp030.png}
    \end{figure}
  }
  \only<30>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp032.png}
    \end{figure}
  }
\end{center}
\end{frame}

@@

    \pause{}

    \begin{figure}
        \includegraphics[scale=0.44]{figures/xkcd_star.png}
        \caption*{Thanks to \textsc{xkcd} we can rule out $36^\circ$ as a primitive.}
    \end{figure}
